---
title: "Homework 1"
author: "Write Your Name and Student ID Here!"
---

```{r global_options, include=FALSE}
# Do not delete or modify this chunk.
# We will cover chunk options later.
# This is required for Question 7
library(knitr)
opts_chunk$set(fig.align="center", fig.height=4, fig.width=5.5)
```

**Question 1** With Markdown write a sentence that has one word in bold.
This is **bold**.


**Question 2** With Markdown write a sentence that has one word in italic.

This is *italic*

**Question 3** With Markdown write a sentence that has one word in italic bold.

This is ***italic bold***.

**Question 4** With Markdown write an unordered list with three items.

This is **bold** ***and*** *italic*

**Question 5** With Markdown write an ordered list with three items.
This **bold** *italic* ***and ordered***

**Question 6** With Markdown give a link to your favorite webpage.
This (https://www.ankara.edu.tr/).

**Question 7** With Markdown add a cat picture.
 https://images.unsplash.com/photo-1529778873920-4da4926a72c2?ixlib=rb-4.0.3&ixid=MnwxMjA3fDB8MHxzZWFyY2h8Mnx8Y3V0ZSUyMGNhdHxlbnwwfHwwfHw%3D&w=1000&q=80

**Question 8** With Rmarkdown insert a code chunk and give an example of a simple mathematical calculation in it.

$\sum_{n=2}^{14} n^2$

**Question 9** With $LaTeX$ write your favorite equation in block form.

$e=mc^2$.

**Question 10** In a code chunk calculate 3 + 4.
```{r}
result <- 3 + 4
print(result)
```